A comparison of classification algorithms applied to the Adult Database

### 2009-12-16 demo/demo.tex
added ilp slides.

\documentclass[xcolor=dvipsnames,professionalfonts,smaller,presentation]{beamer} 
\usecolortheme[named=Brown]{structure} 
\useoutertheme{miniframes}
\usetheme{Malmoe}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage[portuguese]{babel}
\usepackage[latin1]{inputenc}
\usepackage{alltt}
\usepackage{moreverb}
\usepackage{hyperref}
\usepackage{indentfirst}
\usepackage{lastpage}
\usepackage{array}
\usepackage{url}
\usepackage{float}
\usepackage{subfigure}

@@

>>>>

\documentclass[xcolor=dvipsnames,professionalfonts,smaller,presentation]{beamer} 
\usecolortheme[named=Brown]{structure} 
\useoutertheme{miniframes}
\usetheme{Malmoe}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage[portuguese]{babel}
\usepackage[latin1]{inputenc}
\usepackage{alltt}
\usepackage{moreverb}
\usepackage{hyperref}
\usepackage{indentfirst}
\usepackage{lastpage}
\usepackage{array}
\usepackage{url}
\usepackage{float}
\usepackage{subfigure}
\usepackage{multirow}

@@

\subsection{ILP}
\frame[containsverbatim]
{
    \frametitle{ILP}

    \begin{itemize}
    \item Aleph was used to genereate logic clauses.
    \item Uses inverse entailment to generate the bottom clause.
    \item The search for the best clause is implemented by a restricted branch-and-bound algorithm.
    \item The generation of hypothesis takes around 6 hours and produces an error rate on the test set of around 20\%.
    \item Some interesting clauses:
    \end{itemize}

\scriptsize
\begin{verbatim}
more_than_50K(A) :- middle_aged(A), very_high_capital_gain(A), 
                    is_native_of_united_states(A).
more_than_50K(A) :- education_prof_school(A), wife(A), workaholic(A).
more_than_50K(A) :- senior(A), work_private(A), very_high_capital_gain(A).
more_than_50K(A) :- senior(A), work_federal_gov(A), education_doctorate(A).
more_than_50K(A) :- education_doctorate(A), medium_capital_loss(A), workaholic(A).
more_than_50K(A) :- work_self_emp_inc(A), high_capital_gain(A), full_time_worker(A).
more_than_50K(A) :- middle_aged(A), education_masters(A), is_native_of_iran(A).
more_than_50K(A) :- senior(A), full_time_worker(A), is_native_of_cambodia(A).
\end{verbatim}
\normalsize
}
